Descriptive, not injunctive, social norms caused increases in mask wearing throughout the COVID-19 pandemic

### 2022-10-13 appendix.Rmd
update analysis with t16, t17, and t18

```{r plotAttrition, echo=F, fig.width=5, fig.height=3, fig.cap="(ref:plotAttritionCaption)"}
plot2
```

@@

(ref:plotNormCompareCaption) _Predictions from multilevel model of the difference between the perceived strength of descriptive and injunctive social norms._ Points and error bars represent estimated marginal means and 95% confidence intervals, respectively.

```{r plotNormCompare, echo=F, fig.width=3.5, fig.height=3.5, fig.cap="(ref:plotNormCompareCaption)"}
plot7
```

@@

(ref:modelSummaryTable2Caption) Unstandardized fixed effect parameters from multilevel model: difference between perceived strength of descriptive and injunctive social norms. _Standard errors are included in brackets._

```{r modelSummaryTable2, echo=F, warning=F, message=F, results="asis"}
export_summs(m3.1, stars = NULL,
             coefs = c("Intercept" = "(Intercept)",
                       "Difference between norm types" = "varInjNorms")) %>% 
  set_caption("(ref:modelSummaryTable2Caption)") %>%
  set_label("tab:modelSummaryTable2")
```

>>>>

```{r plotAttrition, echo=F, fig.width=5.5, fig.height=3, fig.cap="(ref:plotAttritionCaption)"}
plot2
```

@@

@@
